---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# aiR

<!-- badges: start -->
[![Lifecycle: experimental](https://img.shields.io/badge/lifecycle-experimental-orange.svg)](https://www.tidyverse.org/lifecycle/#experimental)
[![CRAN status](https://www.r-pkg.org/badges/version/aiR)](https://CRAN.R-project.org/package=aiR)
<!-- badges: end -->

aiR is an [R](https://www.r-project.org) package for querying and retrieving air quality information from [AirNow](https://www.airnow.gov) via the [AirNow API](https://airnowapi.org).
Current and historical readings as well as forecasts can be retrieved as tidy data frames.


## Installation

This package is changing rapidly, so it's not quite ready for CRAN.

## Development version

To get a bug fix or to use a feature from the development version, you can install the development version of aiR from GitHub.

```r
# install.packages("remotes")
remotes::install_github("briandconnelly/aiR")
```

## Creating an API Token

The [AirNow API](https://airnowapi.org) is generally free to use.
The `use_airnow()` function can be used to help you create and configure your API token.

```r
aiR::use_airnow()
```


## Air Quality in Seattle

The AirNow API allows you to query air conditions either by ZIP code or latitude/longitude.
Here, we'll get the current conditions in Seattle by ZIP code:

```{r Air conditions in Seattle}
library(aiR)

get_conditions(zip = 98101)
```

## Code of Conduct

Please note that the aiR project is released with a [Contributor Code of Conduct](https://contributor-covenant.org/version/2/0/CODE_OF_CONDUCT.html).
By contributing to this project, you agree to abide by its terms.
